\begin{abstract}
    As cyber threats grow in complexity and scope, traditional security measures prove increasingly inadequate. This paper presents an advanced intelligent detection tool tailored to address these evolving threats through a sophisticated multi-layer network threat graph. This innovative tool amalgamates data from network traffic, intrusion detection systems, and system logs to provide a comprehensive view of network security dynamics. Leveraging state-of-the-art artificial intelligence technologies, including machine learning and deep learning, the tool excels in identifying both known and emerging security threats. It achieves this by analyzing extensive datasets to detect abnormal behaviors and anomalous network patterns. The resulting multi-layer threat graph not only depicts network connections and anomalies visually but also significantly augments the ability of security teams to rapidly comprehend and respond to security threats. This abstract details the design, development, and practical application of the intelligent detection tool, emphasizing its efficacy in converting raw data into actionable security insights via sophisticated AI-driven analysis and visualization techniques. The proposed approach enhances immediate threat detection and facilitates strategic security planning and risk assessment.

    \textbf{Keywords:} Cybersecurity, Network Threat Analysis, Artificial Intelligence, Machine Learning, Deep Learning, Data Visualization, Threat Detection.

\end{abstract}
