\section{Introduction}
As network attacks become increasingly sophisticated and diversified, traditional security measures struggle to comprehensively address emerging threats. In response, the development of an intelligent detection tool that offers a deep and comprehensive perspective has become an urgent need in the field of cybersecurity. The tool introduced in this paper is designed and developed to meet this requirement. It aims to create a multi-layer network threat graph by analyzing network traffic from endpoint devices, event logs from intrusion detection systems (NIDS), and system logs from monitoring devices, providing a holistic view of network security status. This design enables security analysts to understand the security condition of networks from multiple dimensions, thereby more effectively identifying and responding to potential security threats.

The core challenge addressed by the intelligent detection tool lies in utilizing advanced artificial intelligence technologies for deep analysis of vast amounts of network data. This includes employing machine learning algorithms to differentiate abnormal network packets, identify hosts with anomalous behaviors, and analyze clusters of such behaviors. These technologies allow the tool not only to detect known security threats but also to identify unknown or covert threats that traditional security solutions might overlook.

Moreover, the intelligent detection tool presents complex analysis results in a multi-layered, visualized form. This multi-layer threat graph not only shows the connections between nodes in the network but also highlights abnormal events, hosts with unusual behaviors, and the distribution of these abnormal clusters. Such visualization provides an intuitive and easy-to-understand means for security teams to quickly grasp the overall security situation of the network and identify patterns of vulnerabilities and attack behaviors. Additionally, the multi-layer threat graph offers various event entry points, allowing security analysts to analyze and assess from multiple perspectives, whether tracking specific security events, analyzing overall network communication behavior patterns, or even the attack propagation paths of malicious behaviors. This tool provides rich information and deep insights, revealing the structure and characteristics of abnormal network activities, assisting security teams in discovering potential attack paths, and timely adjusting and optimizing network security strategies.

This report focuses on introducing and explaining the design, development, and implementation of the intelligent detection tool, aiming to provide organizations with a comprehensive view of network security status through a multi-layer network threat graph. This tool combines the latest artificial intelligence technologies, including machine learning and deep learning algorithms, as well as big data analytics techniques, to conduct in-depth analysis of data collected from various sources. The report will cover key areas and technologies such as data preprocessing, AI analysis techniques, and the generation and visualization of multi-layer network threat graphs, showcasing the development process, implementation strategy, and practical benefits of the tool. This provides readers with a clear understanding and application framework for leveraging multilayer threat graph detection techniques for correlation and risk assessment of heterogeneous data.
