\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\pagestyle{plain}
\usepackage{placeins}
\usepackage{wrapfig}
\usepackage{stfloats}
\begin{document}

\title{Leveraging Multilayer Threat Graph Detection Techniques for Correlation and Risk Assessment}


\author{\IEEEauthorblockN{1\textsuperscript{st} YuCheng Lin}
    \IEEEauthorblockA{\textit{Department of Information and Finance Management} \\
        \textit{National Taipei University of Technology}\\
        Taipei, Taiwan \\
        t109ab0752@ntut.org.tw}
    \and
    \IEEEauthorblockN{2\textsuperscript{nd} PoTing Lu}
    \IEEEauthorblockA{\textit{Computer Science and Information Engineering} \\
        \textit{Fu Jen Catholic University}\\
        Taipei, Taiwan \\
        amos040425@outlook.com}
    \and
    \IEEEauthorblockN{3\textsuperscript{rd} YuJie Wang}
    \IEEEauthorblockA{\textit{Computer Science and Information Engineering} \\
        \textit{Ming Chuan University}\\
        Taipei, Taiwan \\
        a844536170@gmail.com}
    \and
    \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
        \textit{name of organization (of Aff.)}\\
        City, Country \\
        email address or ORCID}
    \and
    \IEEEauthorblockN{Falcon Wang}
    \IEEEauthorblockA{\textit{ATD} \\
        \textit{WNC}\\
        Hsinchu, Taiwan \\
        falcon.wang@wnc.com.tw}
    \and
    \IEEEauthorblockN{Eric Mao}
    \IEEEauthorblockA{\textit{ATD} \\
        \textit{WNC}\\
        Hsinchu, Taiwan \\
        eric.mao@wnc.com.tw}
}

\maketitle

\input{abstract.tex}

\begin{IEEEkeywords}
    Threat Detection, Graph Theory, Risk Assessment, Multilayer Analysis
\end{IEEEkeywords}

\input{intro.tex}

\input{related.tex}

\input{arch.tex}

\input{exps.tex}

\input{conc.tex}

\begin{thebibliography}{00}
    \bibitem{1} J. Lan, Y. Li, B. Li, and X. Liu, ``Matter: A Multi-Level Attention-Enhanced Representation Learning Model for Network Intrusion Detection,'' in \textit{IEEE International Conference on Trust, Security and Privacy in Computing and Communications (TrustCom)}, Los Alamitos, CA, USA, IEEE Computer Society, pp. 111--116, Dec. 2022.
    \bibitem{2} D. Mudzingwa et al., ``A Study of Methodologies Used in Intrusion Detection and Prevention Systems (IDPS),'' in \textit{2012 Proceedings of IEEE Southeastcon}, pp. 1--6, Mar. 2012.
    \bibitem{3} S. Walling and S. Lodh, ``A Survey on Intrusion Detection Systems: Types, Datasets, Machine Learning Methods for NIDS and Challenges,'' in \textit{13th International Conference on Computing Communication and Networking Technologies (ICCCNT)}, pp. 1--7, Oct. 2022.
    \bibitem{4} P. V. Pandit et al., ``Implementation of Intrusion Detection System Using Various Machine Learning Approaches with Ensemble learning,'' in \textit{2023 International Conference on Advancement in Computation and Computer Technologies (InCACCT)}, pp. 468--472, May 2023.
    \bibitem{5} J. Straub, ``Modeling Attack, Defense and Threat Trees and the Cyber Kill Chain, ATT‘I\&’CK and STRIDE Frameworks as Blackboard Architecture Networks,'' in \textit{2020 IEEE International Conference on Smart Cloud (SmartCloud)}, pp. 148--153, Nov. 2020.
    \bibitem{6} T. N. Kipf and M. Welling, ``Semi-supervised Classification with Graph Convolutional Networks,'' \textit{arXiv preprint arXiv:1609.02907}, Sept. 2017.
    \bibitem{7} M. Safaei Pour, C. Nader, K. Friday, and E. Bou-Harb, ``A Comprehensive Survey of Recent Internet Measurement Techniques for Cyber Security,'' \textit{Computers \& Security}, vol. 128, pp. 103123, 2023, doi: https://doi.org/10.1016/j.cose.2023.103123.
    \bibitem{8} Park J.H., Rathore S., Singh S.K., Salim M.M., Azzaoui A., Kim T.W., Pan Y., Park J.H., ``A Comprehensive Survey on Core Technologies and Services for 5G Security: Taxonomies, Issues, and Solutions,'' \textit{Human-Centric Computing and Information Sciences}, vol. 11, article 3, 2021.
    \bibitem{9} Gupta S., Parne B.L., Chaudhari N.S., ``Security Vulnerabilities in Handover Authentication Mechanism of 5G Network,'' in \textit{Proceedings of the 2018 First International Conference on Secure Cyber Computing and Communication (ICSCCC)}, Jalandhar, India, pp. 369-374, Dec. 2018.
    \bibitem{10} Borgaonkar R., Tøndel I.A., Degefa M.Z., Jaatun M.G., ``Improving Smart Grid Security Through 5G Enabled IoT and Edge Computing,'' \textit{Concurrency and Computation: Practice and Experience}, vol. 33, e6466, 2021.
    \bibitem{11} Gonzalez A.J., Grønsund P., Dimitriadis A., Reshytnik D., ``Information Security in a 5G Facility: An Implementation Experience,'' in \textit{Proceedings of the 2021 Joint European Conference on Networks and Communications \& 6G Summit (EuCNC/6G Summit)}, Porto, Portugal, pp. 425-430, June 2021.
    \bibitem{12} Nalendra, A. ``Rapid Application Development (RAD) model method for creating an agricultural irrigation system based on internet of things,'' in \textit{Proceedings of the IOP Conference Series: Materials Science and Engineering}, Sanya, China, IOP Publishing: Bristol, UK, vol. 1098, p. 022103, Nov. 2021.
    \bibitem{13} Chun, J.; Lee, J.; Kim, J.; Lee, S., ``An international systematic review of cyberbullying measurements,'' \textit{Comput. Hum. Behav.}, vol. 113, 106485, 2020.
    \bibitem{14} Wu, J.; Zhang, C.; Liu, Z.; Zhang, E.; Wilson, S.; Zhang, C., ``Graphbert: Bridging graph and text for malicious behavior detection on social media,'' in \textit{Proceedings of the 2022 IEEE International Conference on Data Mining (ICDM)}, Orlando, FL, USA, pp. 548–557, Nov.-Dec. 2022.
    \bibitem{15} Alkhalil, Z.; Hewage, C.; Nawaf, L.; Khan, I., ``Phishing attacks: A recent comprehensive study and a new anatomy,'' \textit{Front. Comput. Sci.}, vol. 3, 563060, 2021.
    \bibitem{16} Liu, Q.; Hagenmeyer, V.; Keller, H.B., ``A review of rule learning-based intrusion detection systems and their prospects in smart grids,'' \textit{IEEE Access}, vol. 9, pp. 57542–57564, 2021.
    \bibitem{17} Rezaimehr, F.; Dadkhah, C., ``A survey of attack detection approaches in collaborative filtering recommender systems,'' \textit{Artif. Intell. Rev.}, vol. 54, pp. 2011–2066, 2021.
    \bibitem{18} Zhang K, Liu J, ``Review on the application of knowledge graph in cyber security assessment,'' in \textit{IOP Conference Series: Materials Science and Engineering}, IOP Publishing, vol. 768, p. 052103, 2020.
    \bibitem{19} Sikos LF, ``AI-powered cybersecurity: from automated threat detection to adaptive defense,'' \textit{CISO Mag}, vol. 4, no. 5, pp. 74–87, 2020.
    \bibitem{20} Sikos LF, Philp D, Stumptner M, et al., ``Visualization of conceptualized dynamic network knowledge for cyber-situational awareness,'' in \textit{Proceedings of the 8th International Conference on Concept Mapping}, p. 396, 2018.
    \bibitem{21} Johnson JH, ``Embracing n-ary relations in network science,'' in \textit{Advances in Network Science}, Springer, Cham, pp. 147–160, 2016.
    \bibitem{22} Sikos LF, Stumptner M, Mayer W, et al., ``Representing network knowledge using provenance-aware formalisms for cyber-situational awareness,'' \textit{Procedia Comput. Sci.}, vol. 126, pp. 29–38, 2018.
    \bibitem{23} Garae J, Ko RKL, ``Visualization and data provenance trends in decision support for cybersecurity,'' in \textit{Data Analytics and Decision Support for Cybersecurity}, Springer, Cham, pp. 243–270, 2017.
    \bibitem{24} Hublikar, Shivaraj and Shet, N. Shekar V., ``Malicious encrypted network traffic flow detection using enhanced optimal deep feature selection with DLSTM,'' \textit{International Journal of Modeling, Simulation, and Scientific Computing}, vol. 15, no. 01, pp. 2450011, 2024. DOI: 10.1142/S1793962324500119.
    \bibitem{25} Estan, C. and Varghese, G., ``New directions in traffic measurement and accounting: Focusing on the elephants, ignoring the mice,'' \textit{ACM Trans. Comput. Syst.}, vol. 21, no. 3, pp. 270–313, 2003.
    \bibitem{26} Eshete, B. and Venkatakrishnan, V. N., ``Dynaminer: Leveraging offline infection analytics for on-the-wire malware detection,'' in \textit{DSN. IEEE}, 2017, pp. 463–474.
\end{thebibliography}

\vspace{12pt}
\end{document}